Resurgence of the Airy function

### 2022-07-07 airy-resurgence.tex
Try solving in Hardy spaces

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}}
\DeclareMathOperator{\Ai}{Ai}

@@

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Action on integral operators}\label{L-int-op}
When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$.
\subsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\begin{align*}
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
\end{align*}
we learn that
\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
\subsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\begin{align*}
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
\end{align*}
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
\section{Integro-differential equations}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

@@

\color{SeaGreen}
\begin{prop}\label{prop:frac-mollify}
If $f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^\alpha)$ with $\alpha \in (-1, \infty)$, then $\partial^\lambda_{\zeta \text{ from } 0}\,f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^{\alpha-\lambda})$ for all $\lambda \in (-\infty, 0)$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{SeaGreen}
\begin{prop}\label{prop:frac-int-growth}
For any $f \in \holoL{\infty}(\Omega)$ and $\lambda \in (-\infty, 0)$, the bound
\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\,f\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \|f\|_\infty \]
holds pointwise throughout $\Omega$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{black}

>>>>

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
\DeclareMathOperator{\Ai}{Ai}

@@

The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Action on integral operators}\label{L-int-op}
When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
for all $\lambda \in (0, \infty)$.
\subsection{Change of translation chart}\label{translation}
Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
we learn that
\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
\subsection{Rescaling of translation structure}
Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$. The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure. The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$. From the calculation
\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
& = \mu\,\laplace_{\zeta, 0} \varphi
we learn that
\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure. We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
\section{Integro-differential equations}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Let $D \subset \C$ be an open disk of radius $R$ whose boundary $\partial D$ contains $\zeta = 0$. The Hardy space $H^p(D)$ is the space of holomorphic functions on $D$ which converge pointwise, almost everywhere, to $L^p$ functions on $\partial D$~\cite[Theorem~3.8]{intro-harmonic}. Its norm $\|\cdot\|_p$ is the $L^p$ norm on $\partial D$ with respect to the rotation-invariant probability measure.

We'll study integral operators $\mathcal{G} \acts H^p(D)$ of the form
\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path. The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$. Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}. That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.

\color{SeaGreen}
Assume $p \le q$.

Functions that extend continuously to $\partial D$ are dense in $H^p(D)$ \textcolor{magenta}{[check]}.
\color{black}

\begin{align*}
\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left|\int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& \le \int_{a \in \partial D} \left(\int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
\end{align*}
Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Then, by H\"{o}lder's inequality,
\begin{align*}
\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
\end{align*}
Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
\begin{align*}
\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
\end{align*}
which simplifies to
\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
That means
\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.

\color{DodgerBlue}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.

@@

\color{SeaGreen}
\begin{prop}\label{prop:frac-mollify}
If $f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^\alpha)$ with $\alpha \in (-1, \infty)$, then $\partial^\lambda_{\zeta \text{ from } 0}\,f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^{\alpha-\lambda})$ for all $\lambda \in (-\infty, 0)$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{SeaGreen}
\begin{prop}\label{prop:frac-int-growth}
For any $f \in \holoL{\infty}(\Omega)$ and $\lambda \in (-\infty, 0)$, the bound
\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\,f\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \|f\|_\infty \]
holds pointwise throughout $\Omega$.
\end{prop}
\color{magenta}
\begin{proof}
??????
\end{proof}
\color{DodgerBlue}
